Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-07-15 sports_analytics.Rmd
small fix

wp_plot + 
  annotation_raster(logos[[1]], -1010, -1490, 0.76, 0.865) + 
  annotation_raster(logos[[2]], -1010, -1490, 0.135, 0.24) + 
  scale_x_reverse()
```

@@

Analytical work in sports requires facility with an ever-changing set of computational tools for working with data. 
Sources of authoritative data about sports are myriad, and are too numerous to list here. 
Software tools for sports analytics are similarly numerous. 
For R, we maintain a [CRAN Task View for Sports Analytics](https://CRAN.R-project.org/view=SportsAnalytics) that catalogs R packages published on the Comprehensive R Archive Network and organizes them by sport [@baumer2022ctv].
A more general collection of software tools is being curated by the SportsDataverse.org (<https://sportsdataverse.org>).

@@

# we could plot greg's chess moves
# doesn't work for me... python/reticulate issues
library(chessR)
us <- c("fatgreggy")
greg <- get_raw_chessdotcom(
  usernames = us,
  year_month = 202206
)

>>>>

wp_plot + 
  annotation_raster(logos[[1]], -1010, -1490, 0.76, 0.865) + 
  annotation_raster(logos[[2]], -1010, -1490, 0.135, 0.24) + 
  scale_x_reverse(breaks = seq(0, 3600, 900))
```

@@

Analytical work in sports requires facility with an ever-changing set of computational tools for working with data. 
Sources of authoritative data about sports are myriad, and are too numerous to list here. 
Software tools for sports analytics are similarly numerous. 
For R, we maintain a [CRAN Task View for Sports Analytics](https://CRAN.R-project.org/view=SportsAnalytics) that catalogs R packages published on the Comprehensive R Archive Network and organizes them by sport [@baumer2022ctv].
A more general collection of software tools is being curated by the SportsDataverse initiative [@gilani2022sportsdataverse].

@@

library(chessR)
us <- c("fatgreggy")
greg <- get_raw_chessdotcom(
  usernames = us,
  year_month = 202206
)
